\documentclass[letterpaper]{resume}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Jared}{Wasserman}{
\begin{minipage}{0.48\textwidth}
\begin{flushright}
linkedin.com/in/jaredbwasserman \\
github.com/jaredbwasserman
\end{flushright}
\vspace{0pt}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\begin{flushleft}
jaredbwasserman@gmail.com \\
(727) 743-7650
\end{flushleft}
\vspace{0pt}
\end{minipage}
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.27\textwidth} % The left column takes up 27% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Data Streaming}
\descript{Processing}
\begin{itemize}
\item Apache Beam
\item Apache Flink
\item Apache Spark
\end{itemize}

\descript{Queueing}
\begin{itemize}
\item Apache Kafka
\item AWS SQS
\item GCP Pub/Sub
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Databases}
\descript{Relational}
\begin{itemize}
\item Amazon Redshift
\item MySQL
\end{itemize}

\descript{Non-Relational}
\begin{itemize}
\item Elasticsearch
\end{itemize}

\descript{Data Catalog}
\begin{itemize}
\item Amundsen
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Deployments}
\descript{Containers}
\begin{itemize}
\item Argo CD
\item Docker
\item Kubernetes
\end{itemize}

\descript{Automation}
\begin{itemize}
\item Ansible
\item Jenkins
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Clouds}
\begin{itemize}
\item AWS
\item Azure
\item GCP
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Languages}
\begin{itemize}
\item C\#
\item C++
\item Java
\item JavaScript
\item \LaTeX
\item Lua
\item MATLAB
\item Python
\item Scala
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Game Engines}
\begin{itemize}
\item Godot
\item Phaser
\item Unity
\end{itemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.72\textwidth} % The right column takes up 72% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Blizzard Entertainment}{Battle.net Data Platform}
\location{Senior Software Engineer I{\hfill}Feb 2022{\dash}Present{\barspace}Irvine, CA}
\location{Software Engineer{\hfill}Feb 2020{\dash}Feb 2022{\barspace}Irvine, CA}
\begin{itemize}
\item Created a data catalog prototype for Elasticsearch data using Amundsen.
\item Implemented a GeoIP data enrichment job using Apache Beam on GCP Dataflow.
\item Designed and coded a Node.js and MySQL application for configuration management.
\item Wrote Scala code for an Apache Flink application to improve processing and config.
\item Utilized Kubernetes and Helm to manage application deployments.
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Microsoft}{Teams Telemetry}
\location{Software Engineer II{\hfill}Jan 2019{\dash}Jan 2020{\barspace}Bellevue, WA}
\begin{itemize}
\item Wrote Apache Spark Scala code for metrics processing on Azure Databricks.
\item Created a data pipeline to coordinate Spark jobs using Azure Data Factory.
\item Ported Teams performance metrics from a legacy solution to an Apache Spark solution.
\item Worked on a data processing system written using Apache Hadoop and Apache Oozie. 
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Amazon}{Advertising Analytics}
\location{Software Development Engineer I{\hfill}Nov 2016{\dash}Dec 2018{\barspace}Seattle, WA}
\begin{itemize}
\item Improved Java application code for ingesting data into Elasticsearch.
\item Wrote Redshift SQL queries for automated ETL as well as ad-hoc data investigation.
\item Utilized AWS Lambda along with AWS SQS for building data pipelines.
\item Designed a data quality system to analyze Excel reports for defects.
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{MathWorks}{Computer Science Development Group}
\location{Associate Software Engineer{\hfill}Sep 2015{\dash}Oct 2016{\barspace}Natick, MA}
\begin{itemize}
\item Designed and implemented the 3D image resize MATLAB function \code{imresize3}.
\item Wrote covariance functions for Gaussian Process Regression in MATLAB.
\item Investigated and resolved technical support questions and issues.
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{DiSTI Corporation}{Virtual Training}
\location{Software Engineer I{\hfill}Jun 2015{\dash}Sep 2015{\barspace}Orlando, FL}
\begin{itemize}
\item Learned basic C++ to understand proprietary simulation tools.
\item Analyzed and implemented customer requirements for a custom simulator.
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\runsubsection{UCF}{College of Engineering and Computer Science}
\location{BS, Computer Science{\hfill}Aug 2011{\dash}May 2015{\barspace}Orlando, FL}
\location{Minor, Mathematics{\hfill}Aug 2011{\dash}May 2015{\barspace}Orlando, FL}
\begin{itemize}
\item Earned a 4.0/4.0 GPA.
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Personal Projects
%------------------------------------------------

\section{Personal Projects}

\runsubsection{Web Games}{Multiplayer JavaScript Games}
\location{Author{\hfill}Oct 2021{\dash}Present}
\begin{itemize}
\item Web server with a Node.js backend and a vanilla JavaScript frontend.
\item Has a lobby system and two multiplayer games written using Phaser and Socket.IO.
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Drift}{World of Warcraft Addon}
\location{Author{\hfill}Dec 2019{\dash}Present}
\begin{itemize}
\item Addon written in Lua that enables moving in-game UI frames via clicking and dragging.
\end{itemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

\end{document}
